\LARGE \bf A Pipeline to Assemble (Near-)Collision Footage Datasets

### 2021-03-27 paper.tex
fixed vgg source

In order to evaluate the importance of acquiring data from multiple geographical locations and under varying driving conditions around the world, we have manually collected a dataset of 223 video clips on which we will test the existing collision anticipation model, DSARNN.  This dataset is comprised of 97 positive and 126 negative videos. Most of these videos represent road scenes from North America, Europe and Russia which have noticeably different characteristics than those in Taiwan. To prepare our data we follow the steps outlined by Chan et. al \cite{chan2016anticipating}. Namely, we trim videos such that they are 5 seconds long sampled at 20fps. We trim such that the collision occurs at frame 90, i.e. the first 90 frames are used for collision prediction. This trimming and sampling functionality is provided within a configuration of our pipeline. In our experiments we use the DSARNN model to be trained on features produced by a running a VGG \cite{simonyan2015deep} on each full frame and the cropped objects within the frame and concatenating the output. This is denoted VGG+RNN+F+D-con. in the original publication. We note that this data includes manually annotated bounding boxes, so there will be no error imposed by using automated vehicle detection and localization models.

>>>>

In order to evaluate the importance of acquiring data from multiple geographical locations and under varying driving conditions around the world, we have manually collected a dataset of 223 video clips on which we will test the existing collision anticipation model, DSARNN.  This dataset is comprised of 97 positive and 126 negative videos. Most of these videos represent road scenes from North America, Europe and Russia which have noticeably different characteristics than those in Taiwan. To prepare our data we follow the steps outlined by Chan et. al \cite{chan2016anticipating}. Namely, we trim videos such that they are 5 seconds long sampled at 20fps. We trim such that the collision occurs at frame 90, i.e. the first 90 frames are used for collision prediction. This trimming and sampling functionality is provided within a configuration of our pipeline. In our experiments we use the DSARNN model to be trained on features produced by a running a VGG \cite{DBLP:journals/corr/SimonyanZ14a} on each full frame and the cropped objects within the frame and concatenating the output. This is denoted VGG+RNN+F+D-con. in the original publication. We note that this data includes manually annotated bounding boxes, so there will be no error imposed by using automated vehicle detection and localization models.
